---
title: "R Notebook : Extension School, Report 1"
output: html_notebook
---

Notepook for report 1

# Load the data

```{r}
library(readr)
library(dplyr)
students_answers <- read_csv("raw_data/students.csv", 
    col_types = cols(Agree = col_integer(), 
        Disagree = col_integer(), `Totally Disagree` = col_integer(), 
        `Totally agree` = col_integer(), 
        X1 = col_integer())) %>%
  janitor::clean_names()

professors_answers <- read_csv("raw_data/professors.csv", 
    col_types = cols(Agree = col_integer(), 
        Disagree = col_integer(), `Totally Disagree` = col_integer(), 
        `Totally agree` = col_integer(), 
        X1 = col_integer())) %>%
  janitor::clean_names()

```

# Part 1

## What is the total number of answers obtained from students?

Get the total student answers

```{r}
students_answers %>% 
  mutate(Total = totally_disagree + totally_agree + agree + disagree) %>%
  select(Total) %>%
  sum()
```

## What is the total number of answers obtained from professors?

Get the total student answers

```{r}
professors_answers %>% 
  mutate(Total = totally_disagree + totally_agree + agree + disagree) %>%
  select(Total) %>%
  sum()
```


## Does each question have the same number of answers?

Return true if there is no more than one distinct value for the total number of answer

students_answers %>% 
  mutate(Total = totally_disagree + totally_agree + agree + disagree) %>%
  select(Total) %>%
  distinct() %>%
  count() == 1

# Part 2

## Obtain side-by-side bar charts 

# Part 3