---
title: "R Notebook : Extension School, Report 1"
output: html_notebook
---

Report 1 notebook. see https://www.extensionschool.ch/learn/programs/50-things-you-need-to-know-about-data-v1/subjects/projects-v1/units/report-1-v1

# Load the data

Load data from Likert test from files.

```{r}
library(readr)
library(dplyr)
students_answers <- read_csv("raw_data/students.csv", 
    col_types = cols(Agree = col_integer(), 
        Disagree = col_integer(), `Totally Disagree` = col_integer(), 
        `Totally agree` = col_integer(), 
        X1 = col_integer())) %>%
  janitor::clean_names()

professors_answers <- read_csv("raw_data/professors.csv", 
    col_types = cols(Agree = col_integer(), 
        Disagree = col_integer(), `Totally Disagree` = col_integer(), 
        `Totally agree` = col_integer(), 
        X1 = col_integer())) %>%
  janitor::clean_names()

```

# Part 1

## Find answers count for students

What is the total number of answers obtained from students?

```{r}
students_answers %>% 
  mutate(Total = totally_disagree + totally_agree + agree + disagree) %>%
  select(Total) %>%
  sum()
```

##  Find answers count for professors

What is the total number of answers obtained from professors?

```{r}
professors_answers %>% 
  mutate(Total = totally_disagree + totally_agree + agree + disagree) %>%
  select(Total) %>%
  sum()
```


## Does each question have the same number of answers?

Return true if there is no more than one distinct value for the total number of answer

```{r}
students_answers %>% 
  mutate(Total = totally_disagree + totally_agree + agree + disagree) %>%
  select(Total) %>%
  distinct() %>%
  count() == 1
```

# Part 2

## Obtain side-by-side bar charts 

```{r}
library(ggplot2)
library(tidyr)

## add respondant column and merge professor and student answers
g1 <- mutate(students_answers, "respondant" = "student")
g2 <- mutate(professors_answers, "respondant" = "professor")
all_answers <- rbind(g1 , g2)

## convert columns to rows
plot_data <- all_answers %>%
  gather(key="rating", value="value", totally_agree, agree, disagree, 
         totally_disagree) 

## print data
rate_labels <- c(
  agree = "Agree",
  disagree = "Disagree",
  totally_agree = "Totally agree",
  totally_disagree = "Totally disagree"
)
plot_data %>%
  ggplot(aes(x=rating, y=value, fill=respondant)) +
  geom_bar(stat='identity', position="dodge") +
  facet_wrap(~x1, scales="fixed") + 
  labs(
    x="type_of_response",
    y="count_of_respsonse",
    title="My side-by-side facet chart",
    subtitle="Using facet to show each questions"
  ) + 
  theme_minimal() +
  theme(
      axis.text.x = element_text(angle=90, hjust=0)
      ) +
  scale_x_discrete(labels=rate_labels)


```


# Part 3

## Mode Computing

compute mode for each question

```{r}
plot_data %>%
  group_by(respondant, x1, rating) %>%
  summarise(value=max(value)) %>%
  ungroup() %>%
  group_by(respondant, x1) %>%
  top_n(1,value)

```

























